\documentclass[11pt,letterpaper,oneside]{ucletter}

%if you do not have this package installed, it will be okay.
\usepackage{universityos}
\usepackage{fontspec}
\setmainfont{UCBerkeleyOS.otf}[
BoldFont = UCBerkeleyOSBold.otf ,
ItalicFont = UCBerkeleyOSItalic.otf ,
BoldItalicFont = UCBerkeleyOSBoldItalic.otf ]
\usepackage{xspace}

\name{Dr. Dobbs}
\address{The Standard Position\\
Department of Electrical Engineering and Computer Sciences\\
University of California, Berkeley\\
Berkeley, CA 94720-1774}
\telephone{Tel: +1 (510) 867-5309}
\login{dobbs@EECS.Berkeley.Edu}
\signature{Dr. Dobbs}

%\textheight 645pt
%\textheight 8.4in
%\textwidth 6.4in
%\oddsidemargin 0cm

\begin{document}

\begin{letter}
{Dr. Person-To-Whom\\
Chairperson, Important Committee\\
Mid-Valley Institute of Technology (MIT)}

\opening{Dr. Person-to-Whom,}

This is my letter. I hope you will replace my contents with actual contents pertaining to your discussion. I don't really have a lot to say on this matter, other than it has not certainly been the policy, nor, ever to my knowledge, would be, in other words, of course not considering new policy initiatives, as the President would decide them.

If you are getting errors, you should remove the universityos package, which probably has fonts you do not want.

As you can see, multiple paragraphs are nice, and if you really want, you can have
\begin{itemize}
	\item bullets,
	\item numbers, and
	\item special sentences.
\end{itemize}

And in conclusion, it does \emph{not} say R.S.V.P. on the Statue of Liberty.

\closing{Best regards,}

\end{letter}

\end{document}